---
title: "`ggplot2` Practice Questions"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r}
library(tidyverse)
loans <- read_csv("data/loans.csv")
```

1.1	Make a scatterplot with loan amount on the x-axis and interest rate, on the y-axis again.
```{r}
ggplot(loans) +
  geom_point(aes(loan_amnt, int_rate)) +
  labs(x = "Loan Amount",
       y = "Interest Rate") 

# Resulting visualisation is not that clear due to sheer amount of data.  Biggest takeaway is the high density of low loan amounts with low/medium interest rate. Graph is overloaded in bottom left quadrant.

```

1.2	Add transparency of points to the plot you just created.
```{r}
loans %>% 
ggplot() +
  aes(loan_amnt, int_rate) +
  geom_point(alpha = 1/10) +
  labs(x = "Loan Amount",
       y = "Interest Rate") 

# Changed layout as transparency worked better on line below aes function.
```

1.3	Edit the plot you created to colour the points by the grade of the loan.
```{r}
loans %>% 
ggplot() +
  aes(loan_amnt, int_rate, colour = grade) +
  geom_point(alpha = 1/5) + 
   labs(x = "Loan Amount",
       y = "Interest Rate") 
#  As before but adjusted alpha as previous level was too light with colour added.

```

1.4	Editing the current plot, use faceting to make a separate plot for each grade.
```{r}
loans %>% 
ggplot() +
  aes(loan_amnt, int_rate, colour = grade) +
  geom_point(alpha = 1/10) + 
  facet_wrap(~ grade) +
   labs(x = "Loan Amount",
       y = "Interest Rate") 

# Deicided wrap was best option for faceting, adjusted alpha again as results not that pleasing.
```

2. Make a barplot where the height of the bars show the mean loan amount for each grade. Colour the bars by the mean interest rate in each grade.
```{r}
options(scipen=999)
loans %>% 
  mutate(mean_loan = mean(loan_amnt),
         mean_int = mean(int_rate)) %>% 
  ggplot() +
  aes(grade, loan_amnt, fill = int_rate) +
  geom_col() +
    labs(x = "Grade",
     y = "Average Loan Amount",
     fill = "Avg Int Rate")
#  Feel some of my steps are probably un-necessary here.  Felt I needed a mutate to get the mean but not 100% convinced. Options (scipen) added as numbers were in scientific format initially.
```



3. Explore the data. Try to create one polished graph that summarises how purpose, loan amount, interest rate and grade are related. Is there one purpose that is significantly different from the others? How can you show this in your graph?

<!-- Struggled with this one, tried all manner of plots, bars, etc but couldn't get all variables showing clearly & usefully, tried Shiny as a last resort almost and couldn't get that to work.  Not a good task for me this one! -->

```{r}
library(shiny)

loans %>% 

ui <- fluidPage(
  titlePanel("Loans Breakdown"),

  sidebarLayout(
    sidebarPanel(
      
      selectInput("purpose_input",
        "Loan Purpose",
        choices = purpose
      )
    ),

        mainPanel(
      plotOutput("loans_plot")
    )
  )
)

server <- function(input, output) {
  
  output$loans_plot <- renderPlot({
    loans %>%
      filter(purpose == input$purpose_input) %>%
      filter(grade == input$grade_input) %>%
      ggplot() +
      aes(x = loan_amnt, y = int_rate, fill = grade) +
      geom_col()
  })
  
}

shinyApp(ui = ui, server = server)




