---
title: "Distributions homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---
```{r}
library(tidyverse)
library(janitor)
library(prob)
```

**Question 1.**  
Load the data, `clean_names()` and explore it.
```{r}
mobile_phones <- read_csv("data/20190928-items.csv") %>% 
clean_names() %>% 
  glimpse()
# Small dataset, 800 rows with 9 columns, around half of which are probably irrelevant for the questions to be answered.
# Mainly character columns-->
```

**Question 2.**  
Find the brand with the highest numbers of phones in the dataset.
```{r}
# group by brand, summarise the count, sort in descending order to get an overall picture, then take the top entry 
mobile_phones %>% 
  group_by(brand) %>% 
  summarise(
    count = n()
  ) %>% 
  arrange(desc(count)) %>% 
  head(1)

  
```

**Question 3.**  
For your top brand, plot the distribution of phone ratings as a probability density, overlaying a fitted normal distribution. Do you think the normal distribution provides a good model of these ratings?<br>
```{r}
samsung_ratings <- mobile_phones %>%
  filter(brand == "Samsung") %>% 
  summarise(mean = mean(rating),
            sd = sd(rating)
            )
```


**Question 4.**  
We can be more quantitative in comparing the distribution of top brand ratings with a normal distribution. You calculated the `mean()` and `sd()` of your distribution in an earlier question. Use these values to calculate the *proportions* of ratings within one-, two- and three standard deviations of the mean. Compare these proportions with those you expect for a normal distribution.  



You can use a `filter()` to get only the ratings within one-, two- and three standard deviations of the mean, and then think about how to calculate what proportion each of these filtered sets make of the total number of ratings. You'll need to use three separate `filter()` and `summarise()` pipes to do this.




Here's the code to filter and summarise the proportion of ratings within one standard deviation of the mean.
```{r, eval=FALSE}
samsung_ratings %>%
  filter(rating >= samsung_stats$mean - samsung_stats$sd) %>%
  filter(rating <= samsung_stats$mean + samsung_stats$sd) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_ratings))
```
</details>

# Extension

Investigate the use of the `qqnorm()` plot in R to determine whether data is normally distributed. What is a 'quantile-quantile plot'? What do we expect to see in a `qqnorm()` plot if data is nearly normally distributed?

Here are a few resources:

* [Understanding QQ plots](https://data.library.virginia.edu/understanding-q-q-plots/)
* [Short video tutorial](https://www.youtube.com/watch?v=Erze9pNIX8A) (the presenter doesn't use RStudio, but the commands are the same. Just ignore the final comments on hypothesis tests for now.)
* [Longer video tutorial](https://www.youtube.com/watch?v=smJBsZ4YQZw)
* [Quantile-Quantile plots - R Base Graphs](http://www.sthda.com/english/wiki/qq-plots-quantile-quantile-plots-r-base-graphs)

