---
title: 'Manual model development'
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---


# MVP

# Question 1

Tidy up the data ready for regression:
```{r}
library(tidyverse)
kc <- read_csv("data/kc_house_data.csv") 
glimpse(kc)

# Load data, renamed as kc for King County, glimpse to see what the dataset contains, especially data types,
```
```{r}
kc_tidy <- kc %>% 
  mutate(grade_a = ifelse(grade >= 11, 1, 0)) %>%
  mutate(grade_b = ifelse(grade >= 4 & grade < 11, 1, 0)) %>%
  mutate(grade_c = ifelse(grade < 4, 1, 0)) %>%
  mutate(across(c("waterfront", renovated = "yr_renovated"), as.logical)) %>% 
  select(-c(id, date, grade, yr_renovated, zipcode, sqft_living15, sqft_lot15))
    
#  Data cleaning, binned the grade variable into 3 groups A, B, & C depending on their value. 
#  Corresponds with above standard, standard, and below standard.
#  Changed waterfront & yr_renovated to logical data types, renamed yr_renovated also.
#  Removed variables no longer required or not relevant.
```



# Question 2

Check for aliased variables using the `alias()` function (this takes in a formula object and a data set). [**Hint** - formula `price ~ .` says 'price varying with all predictors', this is a suitable input to `alias()`]. Remove variables that lead to an alias. Check the 'Elements of multiple regression' lesson for a dropdown containing further information on finding aliased variables in a dataset.
```{r}
alias(lm(price ~ ., data = kc_tidy))
```
```{r}
kc_tidy <- kc_tidy %>% 
  select(-c(sqft_basement, grade_c))
  #  Removed 2 variables showing as aliases from first scan, rerun alias below to ensure all were gone.
alias(lm(price ~ ., data = kc_tidy))
```


# Question 3

Systematically build a regression model containing up to **four** main effects

```{r}
kc_tidy_numeric <- kc_tidy %>%
  select_if(is.numeric)

kc_tidy_nonnumeric <- kc_tidy %>%
  select_if(function(x) !is.numeric(x))

kc_tidy_nonnumeric$price <- kc_tidy$price

library(GGally)
ggpairs(kc_tidy_numeric)
ggpairs(kc_tidy_nonnumeric)
```
# Kinda stuck here as diagram is unreadable?
