---
title: "Homework - CIs"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```
```{r}
library(janitor)
library(tidyverse)
library(infer)
```


**Task 1.**  
Load the data again, `clean_names()`, and re-familiarise yourself with it
```{r}
ames <- read_csv("data/ames.csv") %>% 
clean_names
ames
```


**Task 2.**  
Investigate the distribution of `lot_area`. Is the distribution roughly normal? If not, what problems do you find?
```{r}
lot_area <- ames %>%
  summarise(
    count = n(),
    mean = mean(lot_area),
    median = median(lot_area),
    sd = sd(lot_area)
  )
lot_area

lot_area_plot <- ames %>%
  ggplot(aes(x = lot_area)) + 
  geom_histogram(col = "white", fill = "firebrick") +
  labs(x = "Lot Area")

lot_area_plot
# The data is very strongly right skewed, there must an outlier(s) far in excess of the median
```
**Task 3.**  
Compute and visualise a bootstrap sampling distribution for the `mean(lot_area)` of the sold houses.
```{r}
bootstrap_mean_lot_area <- ames %>% 
  rep_sample_n(size = 500, replace = TRUE, reps = 5000) %>% 
  summarise(mean_lot_area = mean(lot_area))

bootstrap_mean_lot_area


```
```{r}
mean_lot_area_plot <- bootstrap_mean_lot_area %>%
  ggplot(aes(x = mean_lot_area)) + 
  geom_histogram(col = "white", fill = "firebrick") +
  labs(x = "Mean Lot Area")

mean_lot_area_plot
```

**Task 4.**  
Use your bootstrap distribution to calculate a $95\%$ CI for `mean(lot_area)`, and visualise it on the distribution
```{r}
infer_ci_95 <- bootstrap_mean_lot_area %>%
  get_confidence_interval(level = 0.95, type = "percentile")

infer_ci_95
```
```{r}
bootstrap_mean_lot_area %>%
  visualise(bins = 30) +
  shade_confidence_interval(endpoints = infer_ci_95)
```



**Task 5.**  
You would like to know the `mean(lot_area)` of the sold houses with higher confidence. Calculate the $99\%$ CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the $95\%$ CI? Does that make sense?

```{r}
ci_99 <- bootstrap_mean_lot_area %>% 
  summarise(
    mean = mean(mean_lot_area),
    lower_bound = quantile(mean_lot_area, probs = 0.005),
    upper_bound = quantile(mean_lot_area, probs = 0.995)
  )
ci_99
# Result makes sense, a wider range gives greater accuracy, greater accuracy needs more data i.e. a wider range of points
```


**Task 6.**  
Calculate the point estimate of the `mean(lot_area)`
```{r}
infer_resample <- ames %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")

mean_lot_area <- infer_resample %>%
  summarise(mean = mean(stat))

mean_lot_area
```



# Extension



**Task 1.**  
Calculate a point estimate and $95\%$ CI for the proportion of houses in the data built before 1920.  Does the number of `reps` you use matter? [Investigate `reps` from $200$ up to $50000$, memory of your laptop permitting].


```{r}
extension_task_50000 <- ames %>%
  filter(year_built < 1920) %>% 
  specify(response = year_built) %>%
  generate(reps = 50000, type = "bootstrap") %>%
  calculate(stat = "mean")

ci_95_50000 <- extension_task_50000%>%
  get_confidence_interval(level = 0.95, type = "percentile")

ci_95_50000
```

