---
title: "Text Mining Homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE, fig.align = "center", message = FALSE, warning = FALSE)
```

# MVP

Using the dataset `austen_books()` from the package `janeaustenr`:

1. Find the most common words in both Pride & Prejudice and Sense & Sensibility.

```{r}
#  Load required libraries
library(tidyverse)
library(tidytext)
library(janeaustenr)
```

```{r}
#  Create new tibbles for each book and unnest tokens
pride_book <- tibble(
  id = 1:length(prideprejudice),
  text = prideprejudice
) %>% 
  unnest_tokens(word, text)

sense_book <- tibble(
  id = 1:length(sensesensibility),
  text = sensesensibility
) %>% 
  unnest_tokens(word, text)
```

```{r}
# Count most common words in Pride & Prejudice
pride_book %>% 
count(word, sort = TRUE)
```
```{r}
# Count most common words in Sense & Sensibility
sense_book %>% 
count(word, sort = TRUE)
```
2. Find the most common words in both Pride & Prejudice and Sense & Sensibility, not including stop words.
```{r}
# Redo previous task but remove stop words via anti-join
pride_book %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>% 
  head(10)
```
```{r}
# Redo previous task but remove stop words via anti-join
sense_book %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>% 
  head(10)
```

3. Find the most common sentiment words in both Pride & Prejudice and Sense & Sensibility.
```{r}
# Create new object of Pride & Prejudice with sentiments counted
pride_sentiments <- pride_book %>%
  inner_join(get_sentiments("afinn")) %>% 
  count(word, sort = TRUE)

pride_sentiments
```
```{r}
# Create new object of Sense & Sensibility with sentiments counted
sense_sentiments <- sense_book %>%
  inner_join(get_sentiments("afinn")) %>% 
  count(word, sort = TRUE)

sense_sentiments
```


# Extension

Taking your results above. Can you create a plot which visualises the differences between the books?  
```{r}
# Load austen_book function, filter the two books required, unnest tokens, group into each book.
#  Create new column to show position of word in the overall book/story arc.
# GGplot using facet_wrap to show side by side graphs

austen_books() %>%
  filter(book %in% c("Pride & Prejudice", "Sense & Sensibility")) %>%
  unnest_tokens(word, text) %>%
  inner_join(get_sentiments("afinn")) %>%
  group_by(book) %>%
  mutate(word_n = row_number()
  ) %>%
    mutate(story_arc = word_n/max(word_n) 
  ) %>% 
ggplot +
  aes(x = story_arc, y = value, colour = book) +
  geom_smooth(se = FALSE) +
  guides(colour = FALSE) +
  facet_wrap(~book, nrow = 5)
```