---
title: "Decision trees homework"
output:
  pdf_document: default
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
```

```{r, warning = FALSE, message = FALSE}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(janitor)
titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```


# MVP 

## Question 1  

```{r}
# View the data
summary(titanic_set)
```

```{r}
# Create new dataset and filter by survival flag
titanic_clean <- titanic_set %>%
  filter(!is.na(survived)) %>% 
# Convert to factor level and select only required columns, remove any other NA's
	mutate(sex = as.factor(sex), 
	       age_status = as.factor(if_else(age <= 16, "Child", "Adult")),
         class = factor(pclass, levels = c(1,2,3), labels = c("Upper", "Middle","Lower")), 
	       survived = factor(survived, levels = c(0,1), labels = c("No", "Yes")), 
	       origin_port = as.factor(embarked)) %>%
  select(sex, age_status, class, origin_port, sib_sp, parch, survived) %>%
  na.omit()
```


## Question 2  

```{r}
titanic_clean %>% 
  ggplot(aes(x = age_status, fill = survived)) + 
  geom_bar() + 
  facet_grid(.~sex) + 
  theme_bw()

# Looking to see the relationship between surviving and age/gender.
# Data shows far higher chance of surviving if female in both adult & child groups.
# Adult males have worst chance of survival and highest amount of overall deaths.
```


```{r}
titanic_clean %>% 
  ggplot(aes(x = class, fill = survived)) + 
  geom_bar() + 
  facet_grid(.~sex) + 
  theme_bw()

# Looking at relationship between surviving and class/gender
# Data shows far higher chance of surviving if female and middle or upper class, lower class women are much more likely to have died.
# In males, the story is different, middle class males are proportionally worse off but lower class males make up the largest total overall.
```

## Question 3  
```{r}
# Get the number of rows to work out the percentage
n_data <- nrow(titanic_clean)

# Create a test sample index at 20% for an 80/20 split, this is a standard split.
test_index <- sample(1:n_data, size = n_data*0.2)

# Create test set
titanic_test  <- slice(titanic_clean, test_index)

# Create training set
titanic_train <- slice(titanic_clean, -test_index)
```

```{r}
# Check test set for balance
titanic_test %>%
 tabyl(survived)
```
```{r}
# Check training set for balance against test set
titanic_train %>% 
  tabyl(survived)
# Both sets are similar at around 50/50 & 60/40 respectively
```
## Question 4      
```{r}
titanic_fit <- rpart(
  formula = survived ~ ., 
  data = titanic_train, 
  method = 'class'
)

rpart.plot(titanic_fit, 
           yesno = 2, 
           fallen.leaves = TRUE, 
           faclen = 6, 
           digits = 4)
```
## Question 5    

# The root node shows a 38.95% chance of NOT surviving, all other factors being equal.
# The variables picked are gender, class, and age as expected. sib_sp has been added though, due to being significant.
# When gender is added to "not surviving", the prediction is that only 19.29% of men will survive, compared to 74.7% of women
# For the women who wouldn't survive 46.25% of them would be in Lower Class, compared to 93.44 of non-Lower Class who would survive 
# The lowest chance of survival seems to be females who have over 3 siblings or spouses with a rate of 0. This could be an anomaly though.
# Regarding the age variable, adults seem to fare better with a predicted survival rate of 76.19% compared to 41.18%


## Question 6     

```{r}
library(modelr)
# Add predictions
titanic_test_pred <- titanic_test %>%
  add_predictions(titanic_fit, type = 'class')
```

```{r}
# Visual check of reasonableness of the survival prediction
titanic_test_pred %>% 
  select(sex, class, sib_sp, age_status, survived, pred)
```
```{r}
# Check model performance
library(yardstick)
conf_mat <- titanic_test_pred %>% 
  conf_mat(truth = survived, estimate = pred)
conf_mat

# Performance check shows a mixed result, false positive rate is high at 31 against true negative of 74.
# True positive rate of 35 is much better against false negative of only 2.
```

```{r}
accuracy <- titanic_test_pred %>%
 accuracy(truth = survived, estimate = pred)
accuracy 
# 76% rate of successful prediction returned
```


```{r}
# For completeness,  caret package used to create a confusion matrix
library(caret)
confusionMatrix(titanic_test_pred$pred, titanic_test_pred$survived)  
```

