---
title: "Simple linear regression homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

# MVP

* Load the data into a dataframe `project`

```{r}
library(tidyverse)
library(broom)
pm <- read_csv("data/project_management.csv")
```

* Plot the data, taking `estimated_length` as the independent variable and `actual_length` as the dependent variable. 
```{r}
pm %>% 
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point()
```

* Calculate the correlation coefficient of `estimated_length` and `actual_length` and interpret the value you obtain.

```{r}
pm %>%
  summarise(cor(estimated_length, actual_length))
  

# <!-- This magnitude suggests a very strong correlation between estimated length & actual length -->
```

* Perform a simple linear regression using `actual_length` as the dependent variable, and `estimated_length` as the independent variable. Save the model object to a variable. 

```{r}
model <- lm(formula = actual_length ~ estimated_length, data = pm)
model
```

```{r}
fitted(model)
```

```{r}
pm %>%
  ggplot(aes(x = estimated_length, y = actual_length)) +
  geom_point() +
  geom_abline(
    intercept = model$coefficients[1],
    slope = model$coefficients[2],
    col = "red"
  )
```

* Interpret the regression coefficient of `estimated_length` (i.e. slope, gradient) you obtain from the model. How do you interpret the $r^2$ value reported by the model?
```{r}
summary(model)
```

* Is the relationship statistically significant? Remember, to assess this you need to check the $p$-value of the regression coefficient (or slope/gradient). But you should first check the regression diagnostic plots to see if the $p$-value will be reliable (don't worry about any outlier points you see in the diagnostic plots, we'll return to them in the extension).

```{r}
tidy(model)
```
