---
title: "R Notebook"
output: html_notebook
---

```{r}
# Titanic Question: Calculate the conditional probabilities prob
# (survived∣crew)and prob(survived∣passenger) to settle this dispute.
library(prob)
library(gtools)
library(tidyverse)

titanic <- read_csv("data/titanic.csv") 
```

```{r}
titanic_tidy <- titanic %>%
   mutate(
    crew = if_else(fare < 1, "TRUE", "FALSE"))
         
```

```{r}
prob_survived_crew <- titanic_tidy %>%
  filter(crew == "TRUE", survived == "yes") %>%
  summarise(prob = n() / nrow(titanic_tidy))
prob_survived_crew
```

```{r}
prob_survived_passenger <- titanic_tidy %>%
  filter(crew == "FALSE", survived == "yes") %>%
  summarise(prob = n() / nrow(titanic_tidy))
prob_survived_passenger 
```

# Question 1.
# If I roll a six-sided dice once, what is the probability of getting a number less than 5?
```{r}
s <- rolldie(1)
size_s <- nrow(s)
less_than_5 <- s %>% 
  filter(X1 < 5)
prob_less_than_5 <- nrow(less_than_5)/size_s
prob_less_than_5
```

# Question 2.
# How many outcomes are there in the sample space of an experiment in which we toss three dice?
```{r}
s <- rolldie(3)
size_s <- nrow(s)
size_s
```
# Question 3.
# In an experiment where we roll four dice:
# How many outcomes are in the event where the total of the four dice equals 5, 6 or 7)?
# what is the probability of this event? # what assumptions do we apply in answering part ii?
```{r}
s <- rolldie(4)
size_s <- nrow(s)
equals_5_6_7 <- s %>% 
  filter(X1 + X2 + X3 + X4 == c("5", "6", "7"))
prob_equals_5_6_7<- nrow(equals_5_6_7)/size_s
equals_5_6_7
```



# Question 4.
# Five chairs are placed in a row in a room, along with five people of differing height. 
# The people sit down randomly on the chairs. 
# What is the probability that they sit in order of decreasing height, left to right?
```{r}

people <- c(1:5)


chairs <- as_tibble(
  permutations(
    n = 5, 
    r = 5, 
    v = people, 
    repeats.allowed = FALSE
  )
)
chairs

# 120 total possibilities so 2 instances in 120 they would sit in height order, left to right specifically means probability is 1 in 120
```

# Question 5.
# I roll six dice:
# what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
# what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
```{r}
s <- rolldie(6)
size_s <- nrow(s)
size_s
# probability is 1 in 46,656 for part 1
size_s / 6
# probability is 1 in 7776 for part 2
```



# Question 6.
# If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?
<!-- 52 cards -->
<!-- 26 are black so 1 in 2 it's black -->
<!-- 13 are spades so probability is 1 in 4 / 0.25 -->


