---
title: "Homework - features and elements of multiple regression"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center')
```

# MVP

1. Load the `diamonds.csv` data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant [Kaggle page](https://www.kaggle.com/shivam2503/diamonds/)
```{r}
library(tidyverse)
diamonds <- read_csv("data/diamonds.csv") %>% 
  glimpse()
```
2. We expect the `carat` of the diamonds to be strong correlated with the physical dimensions `x`, `y` and `z`. Use `ggpairs()` to investigate correlations between these four variables.

```{r}
library(GGally)
ggpairs(diamonds)
```
## x, y, z all have a strong, positive correlation with 'carat' ##


3. So, we do find significant correlations. Let's drop columns `x`, `y` and `z` from the dataset, in preparation to use only `carat` going forward.
diamonds
```{r}
diamonds <- diamonds %>% 
  select(-X1, - x, -y, -z)
# Removed X1 column that was filled in on data import
```


4. We are interested in developing a regression model for the `price` of a diamond in terms of the possible predictor variables in the dataset. 

  i. Use `ggpairs()` to investigate correlations between `price` and the predictors (this may take a while to run, don't worry, make coffee or something).
```{r}
ggpairs(diamonds)
```
# Very high correlation between price & carat, very low correlation between price, depth, & table.  
# Other predictors need further investigation.

  ii. Perform further `ggplot` visualisations of any significant correlations you find.
```{r}

```



5. Shortly we may try a regression fit using one or more of the categorical predictors `cut`, `clarity` and `color`, so let's investigate these predictors. Investigate the levels of these predictors. How many dummy variables do you expect for each of them?
```{r}
diamonds %>% 
  distinct(cut)
# 5 dummy variables required
```
```{r}
diamonds %>% 
  distinct(clarity)
# 8 dummy variables required

```
```{r}
diamonds %>% 
  distinct(color)
# 7 dummy variables required
```
6. Start with simple linear regression. Regress `price` on `carat` and check the regression diagnostics.
```{r}
diamonds %>%
  ggplot(aes(x = price, y = carat)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
```{r}
library(ggfortify)
model <- lm(carat ~ price, data = diamonds)
autoplot(model)
```
```{r}
summary(model)
# Summary shows a high R^ and p numbers look good too, strong correlation confirmed.
```

7. Add another predictor of your choice. Check your assumptions, diagnostics, and interpret the model.
```{r}
model2 <- lm(carat ~ price + cut, data = diamonds)
autoplot(model2) 
```
```{r}
summary(model2)
```
# high, positive correlation adding the 'cut' predictor to carat/price. R^ of .86 confirms this and p number looks good for every entry

    